### 2024-10-17 about/vita.tex
two lectures done
BCS 2025
fixed dyslexia

% For publication lists (adapted from Knuth's algorithms)
\newdimen\itemindent
\newif\ifitempar \itempartrue
\def\itemindentset#1{\setbox0\hbox{{\bf #1.\kern.25em}}\itemindent=\wd0\relax}
\def\pubbegin #1{\itemindentset{#11}} % when all have 1 digit
\def\ppubbegin #1{\itemindentset{#111}} % when 10 or more publications
\def\pubitem#1.{\ifitempar\smallskip\noindent\else\itempartrue
  \hskip-\parindent\fi
  \hbox to\itemindent{\bf\hfil #1.\kern.25em}%
  \hangindent=\itemindent\hangafter=1\ignorespaces}

@@

\newcount\papercount
\papercount=1
\def\papitem{\pubitem P\the\papercount. \global\advance\papercount by -1}
\newcount\submittedcount
\submittedcount=1
\def\subitem{\pubitem S\the\submittedcount. \global\advance\submittedcount by -1}
\newcount\reportcount
\reportcount=1
\def\repitem{\pubitem R\the\reportcount. \global\advance\reportcount by -1}
\newcount\fictioncount
\fictioncount=1
\def\ficitem{\pubitem F\the\fictioncount. \global\advance\fictioncount by -1}

@@

\leftright{\bf NSERC Canada Graduate Scholarship -- Doctoral
\rm (\$105,000)}{\bf September 2023 -- August 2026}
\smallskip
\leftright{\bf FRQNT Bourse de doctorat en recherche
\rm (\$100,000)}{\bf [Declined]}
\smallskip
\leftright{\bf NSERC Canada Graduate Scholarship -- Master's \rm (\$17,500)}{\bf May 2021 -- April 2022}
\smallskip
\leftright{\bf NSERC Undergraduate Student Research Award \rm (\$7,125)}{\bf May -- August 2020}
\smallskip
\leftright{\bf Governor General's Academic Medal -- Bronze}{\bf June 2015}

@@

\sectheader{Published Fiction}

\fictioncount=3
\pubbegin F
\ficitem ``Senang Diri,'' {\sl Existere} {\bf 42},2 (2023), 17--25.
\ficitem ``The Vigil,'' {\sl Ricepaper Magazine} (2023), online.
\ficitem ``Mountain Pass,'' {\sl Prairie Journal of Canadian Literature} {\bf 79} (2023), 48--55.
\endgroup%end the frenchspacing

@@

@@

\starleftright{\bf Teaching assistant}{\bf September 2021 -- present}
\leftright{\sl McGill University}{\sl Montr\'eal, QC, Canada}
\smallskip
Teaching assistant in the following courses. Duties include giving tutorials, holding office hours, and
grading assignments and exams.
\begingroup\parindent=10pt
\smallskip
\thing Winter 2024, Fall 2023: MATH 240 Discrete Structures
\smallskip
\thing Fall 2021: COMP 690 Probabilistic Analysis of Algorithms
\endgroup
\medbreak

>>>>

% For publication lists (adapted from Knuth's algorithms)
\newdimen\itemindent
\newif\ifitempar \itempartrue
\def\itemindentset#1{\setbox0\hbox{{\bf #1.\kern.25em}}\itemindent=\wd0\relax}
\def\pubbegin #1{\itemindentset{#11}} % when all have 1 digit
\def\ppubbegin #1{\itemindentset{#111}} % when 10 or more publications
\def\pubitem#1.{\ifitempar\smallskip\noindent\else\itempartrue
  \hskip-\parindent\fi
  \hbox to\itemindent{\bf\hfil #1.\kern.25em}%
  \hangindent=\itemindent\hangafter=1\ignorespaces}
\def\starpubitem#1.{\ifitempar\smallskip\noindent\else\itempartrue
  \hskip-\parindent\fi
  \llap{*}\hbox to\itemindent{\bf\hfil #1.\kern.25em}%
  \hangindent=\itemindent\hangafter=1\ignorespaces}

@@

\newcount\papercount
\papercount=1
\def\papitem{\pubitem P\the\papercount. \global\advance\papercount by -1}
\newcount\submittedcount
\submittedcount=1
\def\subitem{\pubitem S\the\submittedcount. \global\advance\submittedcount by -1}
\newcount\reportcount
\reportcount=1
\def\repitem{\pubitem R\the\reportcount. \global\advance\reportcount by -1}
\newcount\fictioncount
\fictioncount=1
\def\ficitem{\pubitem F\the\fictioncount. \global\advance\fictioncount by -1}
\def\starficitem{\starpubitem F\the\fictioncount. \global\advance\fictioncount by -1}

@@

\leftright{\bf NSERC Canada Graduate Scholarship -- Doctoral
\rm (\$115,000)}{\bf September 2023 -- August 2026}
\smallskip
\leftright{\bf FRQNT Bourse de doctorat en recherche
\rm (\$100,000)}{\bf [Declined]}
\smallskip
\leftright{\bf NSERC Canada Graduate Scholarship -- Master's \rm (\$17,500)}{\bf May 2021 -- April 2022}
\smallskip
\leftright{\bf NSERC Undergraduate Student Research Award \rm (\$7,125)}{\bf May -- August 2020}
\smallskip
\leftright{\bf Governor General's Academic Medal -- Bronze}{\bf June 2015}

@@

\sectheader{Published Creative Writing {\rm($*$ indicates nonfiction)}}

\fictioncount=4
\pubbegin F
\starficitem ``Lanterns,'' Winner of the 2024 Constance Rooke Creative Nonfiction Prize. To appear in
{\sl The Malahat Review}
\ficitem ``Senang Diri,'' {\sl Existere} {\bf 42},2 (2023), 17--25.
\ficitem ``The Vigil,'' {\sl Ricepaper Magazine} (2023), online. Reprinted in
{\sl Best Canadian Stories 2025} (Windsor, Ont.: Biblioasis, 2024), 244--253.
\ficitem ``Mountain Pass,'' {\sl Prairie Journal of Canadian Literature} {\bf 79} (2023), 48--55.
\endgroup%end the frenchspacing

@@

\starleftright{\bf Course lecturer}{\bf August 2024 -- present}
\leftright{\sl McGill University}{\sl Montr\'eal, QC, Canada}
\smallskip
Instructor for a section of MATH 240 Discrete Structures. Duties include preparing and delivering lectures,
designing assignment and exam questions, and holding office hours.
\medbreak

@@

\starleftright{\bf Teaching assistant}{\bf September 2021 -- April 2024}
\leftright{\sl McGill University}{\sl Montr\'eal, QC, Canada}
\smallskip
Teaching assistant in the following courses. Duties include giving tutorials, holding office hours, and
grading assignments and exams.
\begingroup\parindent=10pt
\smallskip
\thing Winter 2024, Fall 2023: MATH 240 Discrete Structures
\smallskip
\thing Fall 2021: COMP 690 Probabilistic Analysis of Algorithms
\endgroup
\medbreak
